working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-02-24 Manuscript_draft/Manuscript_draft.Rmd
edits methods

[I would explain three test. 0) treatment effects with GLM's, 1) Mantels: relative effects, 2) GLM's or matrix models: Absolute effects and explain them in three independent paragraphs including a rationale of why]()

>>>>

To evaluate heterospecific pollen effect on seed production we performed linear mixed models. The distinct heterospecific pollination treatments were compared with the cross pollination treatment which was our control for optimum seed production for all the species. The different replicates of each treatment were considered as random effects. The changes of seed production per average number of ovules across species were compared through scaling the seed production with mean 0 and standard deviation of 1. All the analysis were conducted with the statistical language `R` `r citep(citation())`

1) Mantels: relative effects

2) GLM's or matrix models
